---
title: "Michael Hornsby EDRM 718 Exercise 10"
output: html_notebook
---

```{r include=FALSE}
library(here)
library(tidyverse)
library(ggrepel)
library(scales)
library(readxl)
library(purrr)
```

Number 1

```{r include=FALSE}
elem <- as.tibble(read_csv(here("data", "Johnson_Elementary.csv")))

elem <- elem[4:220,]
names(elem) <- c("room", "student_id", "tardies;absences",
                 "quarter1", "quarter2", "quarter3", "quarter4")

for (i in 2:nrow(elem)) {
  if (is.na(elem$room[i]) == TRUE) {
    elem$room[i] = elem$room[i-1]
  }
}

elem <- elem[c(-1, -22, -45, -69, -93, -116, -130, -154, -174, -196),]

elem <- elem %>%
  separate(`tardies;absences`, into = c("tardies", "absences"), sep = ";")

elem$tardies <- parse_integer(elem$tardies)
elem$absences <- parse_integer(elem$absences)
elem$quarter1 <- parse_integer(elem$quarter1)
elem$quarter2 <- parse_integer(elem$quarter2)
elem$quarter3 <- parse_integer(elem$quarter3)
elem$quarter4 <- parse_integer(elem$quarter4)

tidy_elem <- elem %>%
  gather(`quarter1`, `quarter2`, `quarter3`, `quarter4`,
         key = "quarter",
         value = "rating")
```

I know this almost certainly isn't the exact way you wanted us to do this
part.  I did these steps becuase I wanted to do EVERY
step in R.  I feel like even a little, easy manipulation of the excel
spreadsheet would have made some of the tidyverse tools more applicable
or straightfoward, but I felt like that may have been cheating.


Number 2

My script for number 2 requires the purrr package (I couldn't tell if the purrr
package was already a part of the tidyverse package or not.
The warning message was a little confusing.).  

```{r}
elem %>% split(elem$room) %>% map(summary)
```


Number 3

```{r}
aggregate(quarter1 ~ room, data=elem, function(x) {sum(is.na(x))}, na.action = NULL)
aggregate(quarter2 ~ room, data=elem, function(x) {sum(is.na(x))}, na.action = NULL)
aggregate(quarter3 ~ room, data=elem, function(x) {sum(is.na(x))}, na.action = NULL)
aggregate(quarter4 ~ room, data=elem, function(x) {sum(is.na(x))}, na.action = NULL)

```


Number 4

```{r}
medians <- aggregate(rating ~ quarter*room, tidy_elem, median)

ggplot(data=medians, aes(x=quarter, y=rating, group=room)) +
  geom_line(aes(color= room)) +
  geom_point() +
  labs(title = "Line Plot of Rating by Quarter with Room Groups")
```


Number 5

```{r}
flights <- as.tibble(read_csv(here("data", "flights.csv")))

key_flights <- flights[(flights$year == 2013) & (flights$dest == 'ATL'), ]

key_flights <- mutate(key_flights, on_time = ifelse(key_flights$arr_delay <= 0, 1, 0))

proportions <- aggregate(on_time ~ carrier, key_flights, mean)

ggplot(data=proportions, aes(carrier, on_time)) +
  geom_col(aes(fill=carrier)) +
  labs(title = "Propoertion of On-Time Flights by Carrier from NYC to ATL in 2013",
       x = "Flight Carrier",
       y = "Proportion of On-Time Flights") +
  scale_fill_discrete(labels = c("Endeavor Air", "Delta Air Lines", 
                                 "Atlantic Southeast Airlines", "AirTran Airways",
                                 "American Eagle Airlines", "United Airlines",
                                 "Southwest Airlines"))

```


